Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-02-03 R0V0.tex
Change statement of the main result.

\begin{theorem}\label{thm:main result}
	If there exists a sum-separable control-contraction metric for system \eqref{eq:general system}, then there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
\end{theorem}

>>>>

\begin{theorem}\label{thm:main result}
	Then, $W$ is a sum-separable control-contraction metric for system \eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
\end{theorem}
